---
output: pdf_document
---
## Statistical Inference Course Project Part 1 ##

Here I will answer the following questions:

The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponential(0.2)s.  
You should  
1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.  
2. Show how variable it is and compare it to the theoretical variance of the distribution.  
3. Show that the distribution is approximately normal.  
4. Evaluate the coverage of the confidence interval for 1/lambda: X¯±1.96Sn√.  

First I calculate the means of a 1000 random exponential with lamba =.2 forty times.

```{r}
install.packages("latex")
library(latex)
set.seed(1234)
samples<-1000
sample_means<-vector("numeric",samples)
rexp(40,.2)
for (i in 1:samples){
  exp_mean<-mean(rexp(40,.2))
  sample_means[i]<-exp_mean
}
sample_means
```

The theoretical mean for an exponential distribution is 1/lamba. in this case lamba is 0.2. So 1/lamba is 5. Therefore the theoretical mean of an exponential with a lamba of 0.2 is 5.

I calculate the mean of the 1000 sample simulation that I run and compare this result to the theoretical mean.

```{r}
total_mean<-mean(sample_means)
total_mean
```

You can see that the simulation mean is pretty close to the theoretical mean.

Next the theoretical standard deviation for the sample means is (1/lamda)/sqrt(1000). Since Lamba in this case is 0.2 the theoretical standard deviation for these sample means is 5/sqrt(1000) or about ,7736102. 

Lets see how this compares to the simualated estimate of the standard deviation of the sampled mean.

```{r}
sd(sample_means)
```

Again the theoretical and simulated values are pretty close.

Now we move onto the third question.
help
